\documentclass[10pt]{article}

\usepackage[top=2cm, bottom=2cm, left=3cm, right=3cm]{geometry}
\usepackage{xcolor}
\usepackage{titlesec}
\usepackage{setspace}
\usepackage{hyperref}
 \hypersetup{colorlinks=true, linkcolor=blue, breaklinks=true, urlcolor=blue, citecolor=blue}
\usepackage{fancyhdr}

\pagestyle{fancy}
\renewcommand{\headrulewidth}{0pt}
\fancyfoot[L]{\small \it Robin Delabays}
\fancyfoot[R]{\small \it \today}

\definecolor{hei}{RGB}{100,25,60}

\titleformat{\section}
{\color{hei}\normalfont\Large}
{\color{red}\thesection}{1em}{}

\begin{document}

\pagenumbering{gobble}

\begin{tabular}{ll}
\begin{minipage}{5cm}
\flushleft
\hspace{-.9cm}
{\Huge\textcolor{hei}{Robin Delabays}}\\
\end{minipage}
& 
\begin{minipage}{9.2cm}
\flushright
\texttt{robindelabays@ucsb.edu}\\
\vspace{1mm}
\texttt{www.delabaysrobin.site}
\end{minipage}
\end{tabular}

\vspace{.3cm}

\begin{center}
\noindent\textcolor{hei}{\rule{.8\textwidth}{1pt}}
\end{center}


\section*{Research experience}

\begin{tabular}{rl}
 \textit{Since Oct. 2020} & \textbf{Post-doctoral scholar} \\
 & Center for Control, Dynamical Systems, and Computation (CCDC), \\ & University of California at Santa Barbara (UCSB). \\
 & {\it Supervised by Prof. Francesco Bullo.} \\
 &\\
 \textit{Oct. -- Dec. 2020} & \textbf{Visiting scholar} \\
 & Mathematics Department, University of Fribourg (Switzerland). \\
 & {\it Invited by Prof. Christian Mazza.} \\
 & \\
 \textit{Mar. -- Jul. 2020} & \textbf{Post-doctoral scholar} \\
 \textit{Aug. -- Dec. 2018} & Institut f\"ur Automatik, ETH Z\"urich. \\
 & {\it Supervised by Prof. Florian D\"orfler.} \\
 &\\
 \textit{Jun. 2018 -- Feb. 2020} & \textbf{Post-doctoral scholar} \\
 & HES-SO Valais//Wallis. \\
 & {\it Supervised by Prof. Philippe Jacquod.} \\
 &\\
 \textit{Jul. -- Aug. 2019} & \textbf{Visiting scholar} \\
 & Center for Nonlinear Studies, Los Alamos National Laboratory. \\
 & {\it Supervised by Dr. Andrey Lokhov and Dr. Marc Vuffray.} \\
\end{tabular}

\section*{Education}
\begin{tabular}{rl}
 \textit{Sep. -- Nov. 2017} & \textbf{Visiting PhD student}\\
 & Institut f\"ur Automatik, ETH Z\"urich.\\
 & {\it Supervised by Prof. Florian D\"orfler.} \\
 &\\
 \textit{Dec. 2014 -- May 2018} & \textbf{PhD in Mathematics} -- \textit{Loop Flows in the Kuramoto Model}\\
 & University of Geneva \& HES-SO Valais//Wallis.\\
 & {\it Supervised by Prof. Yvan Velenik and Prof. Philippe Jacquod.} \\
 &{\footnotesize \tt [\url{archive-ouverte.unige.ch/unige:106921}]} \\
 &\\
 \textit{Sep. 2014} & \textbf{Master thesis}\\
 & University of Geneva.\\
 & The Topological Approach to Phase Transitions.\\
 & {\it Supervised by Prof. David Cimasoni and Prof. Yvan Velenik.} \\
 &\\
 \textit{Sep. 2012 -- Sep. 2014} & \textbf{Master of Science in Mathematics}\\
 & University of Geneva.\\
 & {\it Focus in Topology and Probabilities.} \\
 &\\
 \textit{Sep. 2008 -- Sep. 2011} & \textbf{Bachelor of Science in Mathematics}\\
 & University of Geneva.\\
 & {\it Focus in Topology and Probabilities.}
\end{tabular}

\section*{Teaching and supervision of junior researchers}
\begin{tabular}{rl}
 \textit{Jan. -- Dec. 2019} & \textbf{Andr\'e Reggio} \\
 & Supervision of A. Reggio during his first year of PhD. His work focused on some \\
 & generalization of the Kuramoto model, referred to as \emph{Kuramoto model with} \\
 & \emph{Bounded Confidence}. \\
 &\\
 \textit{Jun. 2019 -- Jul. 2020} & \textbf{Glory M. Givi} \\
 & Supervision of G. M. Givi during her first year of PhD. Her work aims at \\
 & quantifying the robustness of opinions in a group of interacting agents. \\
 &\\
 \textit{May 2018} & \textbf{Guest lecturer} \\ 	
 & Course: Graph Spectral Theory, by Prof. Anders Karlsson, University of Geneva.
\end{tabular}

\section*{Organization of conferences}
\begin{tabular}{rl}
 \textit{Oct. 27, 2020} & \textbf{CCS 2021 - Satellite Symposium} \\
 & Data-based diagnosis of networked dynamical systems \\
 & covering the analysis of networks and disturbances therein relying on measurements. \\
 & Co-organizers: Laurent Pagnier (University of Arizona, Tucson) and \\ 
 & Melvyn Tyloo (University of Geneva). \\
 & {\footnotesize \tt [\url{www.delabaysrobin.site/ccs-satellite}]} \\
 &\\
 \textit{Feb. 2 -- 5, 2020} & \textbf{GeoCoW 2020}  \\
 & Geometry of Complex Webs 2020: Interdisciplinary and international workshop \\
 & covering a wide range of topics related to complex networks and their applications. \\
 & Co-organizers: Matthieu Jacquemet (HES-SO Valais-Wallis and University of \\ 
 & Fribourg) and Christian Mazza (University of Fribourg). \\
 & {\footnotesize \tt [\url{https://sites.google.com/view/geocow2020/home}]} 
\end{tabular}

\section*{Grants and awards}
\begin{tabular}{rl}
 \textit{2020} & \textbf{PostDoc.Mobility}\\
 & Swiss National Science Foundation.\\
 &\\
 \textit{2012} & \textbf{Excellence Master Fellowship}\\
 & University of Geneva.
\end{tabular}


\section*{Personal skills}
\begin{tabular}{rl}
 {\bf Languages} & French (native), English (fluent), German (intermediate), Russian (basic). \\
 &\\
 {\bf Programming} & Julia, Matlab.
\end{tabular}


\newpage

\section*{Publications in peer-reviewed journals}
\subsection*{Preprints}

\begin{itemize}
 \item \textcolor{hei}{\bf R. Delabays}, L. Pagnier, and M. Tyloo,
 \textit{ Locating high-frequency line disturbances with the frequency mismatch},
 submitted (2022).
 {\footnotesize \tt [\url{arxiv.org/abs/2202.08317}]}
 
 \item \textcolor{hei}{\bf R. Delabays}, S. Jafarpour, and F. Bullo,
 \textit{Multistability and Paradoxes in Lossy Oscillator Networks},
 submitted (2022).
 {\footnotesize \tt [\url{arxiv.org/abs/2202.02439}]}
 
 \item \textcolor{hei}{\bf R. Delabays} and M. Tyloo,
 \textit{Heavy-tailed distribution of the number of publications within scientific journals},
 under preparation (2020).
 {\footnotesize \tt [\url{arxiv.org/abs/2011.05703}]} 
\end{itemize}

\subsection*{Peer-reviewed}
\begin{itemize} 
 \item M. Tyloo, \textcolor{hei}{\bf R. Delabays}, and P. Jacquod, 
 \textit{Reconstructing Network Structures from Partial Measurements}, 
 Chaos \textbf{31}, 103117 (2021).  
 {\footnotesize \tt [\url{doi.org/10.1063/5.0058739}], [\url{arxiv.org/abs/2007.16136}]}  

 \item \textcolor{hei}{\bf R. Delabays}, L. Pagnier, and M. Tyloo, 
 \textit{Locating line and node disturbances in networks of diffusively coupled dynamical agents}, 
 New J. Phys. \textbf{23}, 043037 (2021). 
 {\footnotesize \tt [\url{doi.org/10.1088/1367-2630/abf54b}], [\url{arxiv.org/abs/2003.08786}]}

 \item M. Tyloo and \textcolor{hei}{\bf R. Delabays}, 
 \textit{System size identification from sinusoidal probing in diffusive complex networks}, 
 J. Phys. Complex. \textbf{2}, 025016 (2021). 
 {\footnotesize \tt [\url{doi.org/10.1088/2632-072X/abebd3}], [\url{arxiv.org/abs/2009.03824}]}
 
 \item A. Reggio, \textcolor{hei}{\bf R. Delabays}, and P. Jacquod, 
 \textit{Clusterization and phase diagram of the bimodal Kuramoto model with bounded confidence}, 
 Chaos \textbf{30}, 093134 (2020). 
 {\footnotesize \tt [\url{doi.org/10.1063/5.0020436}], [\url{arxiv.org/abs/2007.01214}]}
 
 \item \textcolor{hei}{\bf R. Delabays}, 
 \textit{Dynamical equivalence between Kuramoto models with first- and higher-order coupling},
 Chaos \textbf{29}, 113129 {\bf (2019)}.
 {\footnotesize \tt [\url{doi.org/10.1063/1.5118941}], [\url{arxiv.org/abs/1907.03699}]}
 
 \item \textcolor{hei}{\bf R. Delabays}, M. Tyloo, and P. Jacquod,
 \textit{Rate of Change of Frequency under Line Contingencies in High Voltage Electric Power Networks with Uncertainties}, 
 Chaos \textbf{29}, 103130 (2019). 
 {\footnotesize \tt [\url{doi.org/10.1063/1.5115002}], [\url{arxiv.org/abs/1906.05698}]}
 
 \item M. Tyloo, \textcolor{hei}{\bf R. Delabays}, and P. Jacquod, 
 \textit{Noise-Induced Desynchronization and Stochastic Escape from Equilibrium in Complex Networks}, 
 Phys. Rev. E \textbf{99}, 062213 (2019).
 {\footnotesize \tt [\url{doi.org/10.1103/PhysRevE.99.062213}], [\url{arxiv.org/abs/1812.09497}]}
 
 \item D. Cimasoni and \textcolor{hei}{\bf R. Delabays}, 
 \textit{The Topological Hypothesis for Discrete Spin Models},
 J. Stat. Mech. \textbf{2019} (2019).
 {\footnotesize \tt [\url{doi.org/10.1088/1742-5468/ab0c14}], [\url{arxiv.org/abs/1811.10263}]}
 
 \item \textcolor{hei}{\bf R. Delabays}, P. Jacquod, and F. D\"orfler, 
 \textit{The Kuramoto Model on Oriented and Signed Graphs}, 
 SIAM J. Appl. Dyn. Syst. \textbf{18}, 458 (2019).
 {\footnotesize \tt [\url{doi.org/10.1137/18M1203055}], [\url{arxiv.org/abs/1807.11410}]}

 \item \textcolor{hei}{\bf R. Delabays}, M. Tyloo, and P. Jacquod, 
 \textit{The Size of the Sync Basin Revisited}, 
 Chaos \textbf{27}, 103109 (2017).
 {\footnotesize \tt [\url{doi.org/10.1063/1.4986156}], [\url{http://arxiv.org/abs/1706.00344}]}
 
 \item T. Coletta, \textcolor{hei}{\bf R. Delabays}, and P. Jacquod, 
 \textit{Finite-size Scaling in the Kuramoto Model}, 
 Phys. Rev. E \textbf{95}, 042207 (2017).
 {\footnotesize \tt [\url{doi.org/10.1103/PhysRevE.95.042207}], [\url{arxiv.org/abs/1612.07031}]}
 
 \item \textcolor{hei}{\bf R. Delabays}, T. Coletta, and P. Jacquod, 
 \textit{Multistability of Phase-Locking in Equal-Frequency Kuramoto Models on Planar Graphs}, 
 J. Math. Phys. \textbf{58}, 032703 (2017).
 {\footnotesize \tt [\url{doi.org/10.1063/1.4978697}], [\url{arxiv.org/abs/1609.02359}]}

 \item T. Coletta, \textcolor{hei}{\bf R. Delabays}, I. Adagideli, and P. Jacquod, 
 \textit{Topologically Protected Loop Flows in High Voltage AC Power Grids}, 
 New J. Phys. \textbf{18}, 103042 (2016).
 {\footnotesize \tt [\url{doi.org/10.1088/1367-2630/18/10/103042}], [\url{arxiv.org/abs/1605.07925}]}
 
 \item \textcolor{hei}{\bf R. Delabays}, T. Coletta, and P. Jacquod, 
 \textit{Multistability of Phase-Locking and Topological Winding Numbers in Locally Coupled Kuramoto Models on Single-Loop Networks}, 
 J. Math. Phys. \textbf{57}, 032701 (2016).
 {\footnotesize \tt [\url{doi.org/10.1063/1.4943296}], [\url{arxiv.org/abs/1512.04266}]}
\end{itemize}

\section*{Publications in peer-reviewed conference proceedings}
\begin{itemize}
  \item \textcolor{hei}{\bf R. Delabays} and M. Tyloo,
 \textit{Network Inference using Sinusoidal Probing}, IFAC-PaperOnLine {\bf 54}, 696 (2021).
 {\footnotesize \tt [\url{doi.org/10.1016/j.ifacol.2021.06.131}], [\url{arxiv.org/abs/2002.00490}]}

 \item T. Coletta, \textcolor{hei}{\bf R. Delabays}, L. Pagnier, and P. Jacquod, 
 \textit{Large Electric Load Fluctuations in Energy-efficient Buildings and how to Suppress them with Demand Side Management}, 
 IEEE PES ISGT Conf. Europe (2016).
 {\footnotesize \tt [\url{doi.org/10.1109/ISGTEurope.2016.7856328}], [\url{tinyurl.com/yd59ym5w}]}
\end{itemize}


\section*{Softwares}
\begin{itemize}
 \item \textcolor{hei}{\bf R. Delabays},
 \textit{ADGenerator: Authors Distribution Generator (v1.0)}. Zenodo (2022).
 {\footnotesize \tt [\url{doi.org/10.5281/zenodo.6030303}]}
  
 \item \textcolor{hei}{\bf R. Delabays},
 \textit{DFNSolver: Dissipative Flow Networks Solver (v1.1)}. Zenodo (2022). 
 {\footnotesize \tt [\url{doi.org/10.5281/zenodo.5899408}]}
\end{itemize} 


\section*{Conferences}
All slides and posters can be found on \url{www.delabaysrobin.site}.

\begin{description}
 \item [Oct. 25 -- 29, 2021] Conference on Complex Systems 2021, Lyon, France. \\
 \textcolor{hei}{\bf Oral presentation}: \textit{Flow Network Problems on the $n$-torus with Asymmetric Couplings}.
 
 \item [Jul. 5 -- 10, 2021] Networks 2021, Online. \\
 \textcolor{hei}{\bf Oral presentation}: \textit{Reconstructing Network Structures from Partial Measurements}.
% {\footnotesize \tt [\url{tinyurl.com/b542pw93}]}
 
 \item [Jan. 11 -- 15, 2021] Grid Science Conference, Online. \\
 \textcolor{hei}{\bf Poster}: \textit{Reconstructing Network Structure from Partial Measurements}.
% {\footnotesize \tt [\url{tinyurl.com/3xkxdsyp}]}
 
 \item [Nov. 4 -- 8, 2019] Network Dynamics in the Social, Economic, and Financial Sciences, Torino, Italy. \\
 \textcolor{hei}{\bf Oral presentation}: \textit{Robustness of Elections Results Against External Influence}. 
% {\footnotesize \tt [\url{tinyurl.com/ud9z8v9}]}
 
 \item [Sep. 23 -- 26, 2019] International Workshop on Complex Systems and Networks 2019, Berlin, Germany. \\
 \textcolor{hei}{\bf Oral presentation}: \textit{Rate of Change of Frequency under Line Contingencies}. 
% {\footnotesize \tt [\url{tinyurl.com/y2n6j79j}]}

 \item [Feb. 3 -- 8, 2019] Future Electric Power Systems, Champ\'ery, Switzerland. \\
 \textcolor{hei}{\bf Poster}: \textit{Bounding the Desynchronization Time in Electrical Grids under Fluctuating Sources}.
% {\footnotesize \tt [\url{tinyurl.com/y44w5o84}]}
 
 \item [Jan. 18, 2019] CCDC Seminar, UC Santa Barbara (CA), USA. \\
 \textcolor{hei}{\bf Oral presentation}: \textit{Bounding the Destabilization Time in Networks of Coupled Noisy Oscillators}.
% {\footnotesize \tt [\url{tinyurl.com/ybe4lptp}]}
 
 \item [Jan. 7 -- 11, 2019] Grid Science Conference, Santa Fe (NM), USA. \\
 \textcolor{hei}{\bf Poster}: \textit{Bounding the Desynchronization Time in Electrical Grids under Fluctuating Sources}. 
% {\footnotesize \tt [\url{tinyurl.com/y7hxul4z}]}
 
 \item [Sep. 3 -- 7, 2018] Dynamics Days Europe, Loughborough, United Kingdom. \\
 \textcolor{hei}{\bf Oral presentation}: \textit{Multistability in Electric Power Grids on Meshed, Complex Networks}.
% {\footnotesize \tt [\url{tinyurl.com/ybvjtljp}]}
 
 \item [Jan. 29 -- 31, 2018] 661. WE-Hereaus Seminar, Bad Honnef, Germany. \\
 \textcolor{hei}{\bf Poster}: \textit{The Size of the Sync Basin Revisited}.
% {\footnotesize \tt [\url{tinyurl.com/yaoe9cxz}]}
 
 \item [Sep. 3 -- 8, 2017] International School on Energy Systems, Kloster Seeon, Germany. \\ 
 \textcolor{hei}{\bf Poster}: \textit{Topologically Protected Loop Flows in High Voltage AC Power Grids}.
 
 \item [Feb. 5 -- 9, 2017] Future Electric Power Systems, Champ\'ery, Switzerland. \\ 
 \textcolor{hei}{\bf Oral presentation}: \textit{Loop Flows and the Number of Power Flow Solutions in Meshed Electric Power Grids}.
% {\footnotesize \tt [\url{tinyurl.com/y6vgahv8}]}
 
 \item [Jan. 8 -- 13, 2017] Grid Science Conference, Santa Fe (NM), USA. \\ 
 \textcolor{hei}{\bf Poster}: \textit{Multistability of Phase-Locking and Vortices in Locally Coupled Kuramoto Models}. 
% {\footnotesize \tt [\url{tinyurl.com/ybtbdfqe}]}
 
 \item [Jun. 6 -- 10, 2016] Dynamics Days, Corfu, Greece. \\ 
 \textcolor{hei}{\bf Oral presentation}: \textit{Multistability of Phase-Locking and Topological Winding Numbers in Locally Coupled Kuramoto Models}. 
% {\footnotesize \tt [\url{tinyurl.com/ychnz2c3}]}
\end{description}

\section*{Outreach activities}
 \begin{description}
  \item [Apr. 4 -- 5, 2019] Journ\'ees Culturelles de la Planta, Sion, Switzerland. \\
  \textcolor{hei}{\bf Lecture course to high school students}: \textit{Les statistiques comme outil de manipulation... Comment tricher sans mentir ?}.
  
  \item [Mar. 30, 2017] Journ\'ees Culturelles de la Planta, Sion, Switzerland. \\
  \textcolor{hei}{\bf Lecture course to high school students}: \textit{La Transition \'Energ\'etique}.
 \end{description}


\end{document}
